Properties of Winning Iterated Prisoner's Dilemma Strategies.

### 2023-12-30 paper/main.tex
anonymize manuscript for submission

%%%%Packages%%%%
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{graphics}
\usepackage{multicol}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{color,colortbl}
\usepackage{array}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{wrapfig, blindtext}
\usepackage{soul}
\usepackage{enumerate}
\usepackage[table]{xcolor}
\usepackage{authblk}
%%%%%%%%%%%%%%%%%

@@

\title{Properties of Winning Iterated Prisoner's Dilemma Strategies.}
\author[1, 2]{Nikoleta E. Glynatsi}
\author[2, $\dagger$]{Vincent Knight}
\author[3, $\dagger$]{Marc Harper}

\affil[1]{Max Planck Institute for Evolutionary Biology, Research Group Dynamics of Social
Behavior, Germany}
\affil[2]{Cardiff University, School of Mathematics, UK}
\affil[3]{Google Inc., Mountain View, CA, USA}
\affil[$\dagger$]{V.K. and M.H. contributed equally to this work.}
\date{}

@@

The data set described in this work contains the largest number of \IPD{}
tournaments, to the authors knowledge. The raw data set is available
at~\cite{raw_data} and the processed data at~\cite{data}. Further data mining
could be applied and provide new insights in the field.

@@

The raw and processed datasets have been made publicly available~\cite{data,
raw_data} and can be used for further analysis and insights.

@@

N.G. acknowledges the generous support of the European Research Council Starting
Grant 850529: E-DIRECT and the Max Planck Society.
A variety of open-source software have been used in this work. The authors would
like to express their gratitude to the open-source software community, whose
invaluable contributions significantly enhanced the development and execution of
this research. Namely, the authors would like to thank the developers of the
following software packages: Axelrod-Python library for IPD
simulations~\cite{axelrodproject}, the Matplotlib library for
visualisation~\cite{hunter2007matplotlib}, The Numpy library for data
manipulation~\cite{walt2011numpy}, and finally the scikit-learn library for data
analysis~\cite{scikit-learn}.

>>>>

%%%%Packages%%%%
\usepackage{amsmath}
\usepackage{booktabs}
\usepackage{graphics}
\usepackage{multicol}
\usepackage[ruled,vlined]{algorithm2e}
\usepackage{setspace}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{hyperref}
\usepackage{color,colortbl}
\usepackage{array}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{wrapfig, blindtext}
\usepackage{soul}
\usepackage{enumerate}
\usepackage[table]{xcolor}
\usepackage{authblk}
\usepackage{lineno}
%%%%%%%%%%%%%%%%%

@@

% \linenumbers

\title{Properties of Winning Iterated Prisoner's Dilemma Strategies.}
\author{}
% \author[1, 2]{Nikoleta E. Glynatsi}
% \author[2, $\dagger$]{Vincent Knight}
% \author[3, $\dagger$]{Marc Harper}

% \affil[1]{Max Planck Institute for Evolutionary Biology, Research Group Dynamics of Social
% Behavior, Germany}
% \affil[2]{Cardiff University, School of Mathematics, UK}
% \affil[3]{Google Inc., Mountain View, CA, USA}
% \affil[$\dagger$]{V.K. and M.H. contributed equally to this work.}
\date{}

@@

The data set described in this work contains the largest number of \IPD{}
tournaments, to the authors knowledge. The raw data set and the processed data
have been made available online. Further data mining
could be applied and provide new insights in the field.

@@

The raw and processed datasets have been made publicly available
% ~\cite{data, raw_data} 
and can be used for further analysis and insights.

@@

% N.G. acknowledges the generous support of the European Research Council Starting
% Grant 850529: E-DIRECT and the Max Planck Society.
A variety of open-source software have been used in this work. The authors would
like to express their gratitude to the open-source software community, whose
invaluable contributions significantly enhanced the development and execution of
this research. Namely, the authors would like to thank the developers of the
following software packages: Axelrod-Python library for IPD
simulations~\cite{axelrodproject}, the Matplotlib library for
visualisation~\cite{hunter2007matplotlib}, The Numpy library for data
manipulation~\cite{walt2011numpy}, and finally the scikit-learn library for data
analysis~\cite{scikit-learn}.
